---
title: "MatchReport"
output:
  flexdashboard::flex_dashboard:
    logo: USSF-Primary48.png
    vertical_layout: scroll
    orientation: rows
    css: mytheme.css
editor_options:
  chunk_output_type: console
params:
  pageTitle: "USA v Panama Mar-27-2022" 
  matchName: "USA v Panama : 2022-03-27" 
  matchDate: '2022-03-27' 
  metricNameFull: c("dist", "hml", "hsr", "spr", "exp")
---

```{r setup, include=FALSE}

  library(flexdashboard)
  library(tidyverse)
  library(shiny)
  library(shinydashboard)
  library(reactable)
  library(plotly)
  library(htmltools)
  library(glue)
  library(effectsize)
  library(shinyWidgets)
  library(crosstalk)
  
  visLoc <- "Match Report/vis"

  match10hz <- readRDS(paste0(visLoc,'/match10hz.rds'))
  
  teamMatchDT <- readRDS(paste0(visLoc,'/teamMatchDT.rds'))
  teamHalfDiffDT <- readRDS(paste0(visLoc,'/teamHalfDiffDT.rds'))
  teamMatchPP <- readRDS(paste0(visLoc,'/teamMatchPP.rds'))
  
  athleteMatchPP <- readRDS(paste0(visLoc,'/athleteMatchPP.rds'))
  athleteHalfDiffDT <- readRDS(paste0(visLoc,'/athleteHalfDiffDT.rds'))
  # athleteHalfDT <- readRDS(paste0(visLoc,'/athleteHalfDT.rds'))
  athleteMatchDT <- readRDS(paste0(visLoc,'/athleteMatchDT.rds'))
  
  athleteMatchDur <- readRDS(paste0(visLoc,'/athleteMatchDur.rds'))


```

---
title: `r params$pageTitle`
---

# Match Report {data-orientation="column"}

```{r, echo=F, eval = FALSE}

mainReportDT <- readRDS(paste0(visLoc,'/mainReportDT.rds'))

formation_433 <- function(data, FBLname, FBRname, CBLname, CBRname, CMname, WAMLname, WAMRname, AMLname, AMRname, FWDname, height, width) {

  fluidPage(
      
      # c(10, 20, 10, 20, 10, 20, 10) %>% sum()
      #WAM L
      absolutePanel(
        tags$div(WAMLname, style="text-align: center; font-weight: bold;"),
        data %>% filter(name_display == WAMLname) %>% pull(dt), 
        top = '7%', bottom = NULL, left = '10%', right = NULL, 
        # width = width, height = height, 
        draggable = F, fixed = F,
        style = "border: none !important;"
      ),
      #FWD
      absolutePanel(
       tags$div(FWDname, style="text-align: center; font-weight: bold;"),
        data %>% filter(name_display == FWDname) %>% pull(dt), 
        top = '5%', bottom = NULL, left = '40%', right = NULL, 
        # width = width, height = height,  
        draggable = F, fixed = F,
        style = "border: none !important;"
      ),
      #WAM R
      absolutePanel(
        tags$div(WAMRname, style="text-align: center; font-weight: bold;"),
        data %>% filter(name_display == WAMRname) %>% pull(dt), 
        top = '7%', bottom = NULL, left = NULL, right = '10%', 
        # width = width, height = height, 
        draggable = F, fixed = F,
        style = "border: none !important;"
      ),
      
      #c(17.5,20,2.5,20,2.5,,20,17.5) %>% sum()
      #AM L
      absolutePanel(
        tags$div(AMLname, style="text-align: center; font-weight: bold;"),
        data %>% filter(name_display == AMLname) %>% pull(dt), 
        top = '37%', bottom = NULL, left = '15%', right = NULL, 
        # width = width, height = height, 
        draggable = F, fixed = F,
        style = "border: none !important;"
      ),
      #AM R
      absolutePanel(
        tags$div(AMRname, style="text-align: center; font-weight: bold;"),
        data %>% filter(name_display == AMRname) %>% pull(dt), 
        top = '37%', bottom = NULL, left = NULL, right = '17.5%', 
        # width = width, height = height,  
        draggable = F, fixed = F,
        style = "border: none !important;"
      ),
      
      #c(40, 20, 40) %>% sum()
      #CM
      absolutePanel(
        tags$div(CMname, style="text-align: center; font-weight: bold;"),
        data %>% filter(name_display == CMname) %>% pull(dt),
        top = '42%', bottom = NULL, left = '40%', right = NULL,
        # width = width, height = height,
        draggable = F, fixed = F,
        style = "border: none !important;"
      ),
  
      #c(4, 20, 4, 20, 4, 20, 4, 20, 4) %>% sum()
      #FB L
      absolutePanel(
        tags$div(FBLname, style="text-align: center; font-weight: bold;"),
        data %>% filter(name_display == FBLname) %>% pull(dt),
        top = NULL, bottom = "4%", left = '4%', right = NULL,
        # width = width, height = height,
        draggable = F, fixed = F,
        style = "border: none !important;"
      ),
      #CB L
      absolutePanel(
        tags$div(CBLname, style="text-align: center; font-weight: bold;"),
        data %>% filter(name_display == CBLname) %>% pull(dt),
        top = NULL, bottom = "0%", left = '28%', right = NULL,
        # width = width, height = height, 
        draggable = F, fixed = F,
        style = "border: none !important;"
      ),
      #CB R
      absolutePanel(
        tags$div(CBRname, style="text-align: center; font-weight: bold;"),
        data %>% filter(name_display == CBRname) %>% pull(dt),
        top = NULL, bottom = "0%", left = NULL, right = '28%',
        # width = width, height = height,
        draggable = F, fixed = F,
        style = "border: none !important;"
      ),
      #FB R
      absolutePanel(
        tags$div(FBRname, style="text-align: center; font-weight: bold;"),
        data %>% filter(name_display == FBRname) %>% pull(dt),
        top = NULL, bottom = "4%", left = NULL, right = '4%',
        # width = width, height = height,
        draggable = F, fixed = F,
        style = "border: none !important;"
      )
      
  )
}

shiny::tabsetPanel(
  shiny::tabPanel(title = "Starters",
     formation_433(data = mainReportDT,
      FBLname = 'Antonee Robinson', 
      FBRname = 'Deandre Yedlin', 
      CBLname = 'Miles Robinson', 
      CBRname = 'Walker Zimmerman', 
      CMname = 'Tyler Adams', 
      WAMLname = 'Christian Pulisic', 
      WAMRname = 'Timothy Weah', 
      AMLname = 'Kellyn Acosta', 
      AMRname = 'Yunus Musah',
      FWDname = 'Ricardo Pepi',
      height = 550, width = 300
    )             
  ),
  shiny::tabPanel(title = "Solutions",
     formation_433(data = mainReportDT,
      FBLname = "", 
      FBRname = "Erik Palmer-Brown", 
      CBLname = "Aaron Long", 
      CBRname = "", 
      CMname = "", 
      WAMLname = "Jordan Morris", 
      WAMRname = "", 
      AMLname = "", 
      AMRname = "",
      FWDname = "Jordan Siebatcheu",
      height = 550, width = 300
    )             
  )
)


```

# Team Summary {data-orientation="column"}

## row {data-height="800"}

### Match Comparison

```{r}

 #Plotly Graph
  teamMatchPP %>% layout(height = 800)


```

### Team Match Analytics

```{r}

tabsetPanel(type = "tabs",
  tabPanel("Full Match",teamMatchDT %>% filter(match_half == 'Full') %>% pull(dt)),
  tabPanel("First Half", teamMatchDT %>% filter(match_half == 'First Half') %>% pull(dt)),
  tabPanel("Second Half", teamMatchDT %>% filter(match_half == 'Second Half') %>% pull(dt)),
  tabPanel("Half Dif", teamHalfDiffDT)
)

```

## row

### Team Average Match Intensity

```{r, out.width="100%", eval = FALSE}
 
match10hz %>% filter(athlete_name == 'Team') %>% pull(p) %>% .[[1]]

```

# Athlete Summary {data-orientation="column"}

## row {data-height="1000"}

```{r, eval = TRUE}

athleteNames <- athleteMatchDur %>%
  ungroup() %>%
  rename(athleteName = name_display) %>%
  mutate(
    position = factor(position, levels = c("FB", "CB", "CM", "AM", "WAM", "FWD")),
    played_full = dur == full_match
  ) %>%
  select(position, athleteName, name_last, dur) %>%
  arrange(., position, -dur, name_last) %>%
  as.list()


x <- do.call(tabsetPanel, c(id='t', pmap(athleteNames, function(position, athleteName, name_last, dur) {
  
  tryCatch(expr = {
    
    pp <- athleteMatchPP %>% filter(name_display == athleteName) %>% pull(pp) %>% .[[1]] %>% layout(height = 800)

    DT1 <- athleteMatchDT %>% filter(match_half == 'Full', athlete == athleteName) %>% pull(dt)
    DT2 <- athleteMatchDT %>% filter(match_half == 'First Half', athlete == athleteName) %>% pull(dt)
    DT3 <- athleteMatchDT %>% filter(match_half == 'Second Half', athlete == athleteName) %>% pull(dt)
    DT4 <- athleteHalfDiffDT %>% filter(athlete == athleteName) %>% pull(dt)

    matchDur <- athleteMatchDT %>% filter(athlete == athleteName) %>% pull(data)
    
      tabPanel(
        box_height = '20px',
        title = HTML(glue('<b> {name_last} </b> <br/> <i> <font size="-2"> {position} [{round(dur,0)} min] </font> </i>')),
          fluidPage(
            tags$br(),
            fluidRow(
              column(width = 6,div(style = "height:800px;",
                pp
              )),
              column(width = 6,div(style = "height:800px;",
                tags$br(),
                fluidRow(
                  tabsetPanel(
                    tabPanel("Full Match", DT1),
                    tabPanel("First Half", DT2),
                    tabPanel("Second Half", DT3),
                    tabPanel("Half Diff", DT4)
                  )
                )
              )
            )),
            tags$hr(),
            fluidRow(
              match10hz %>% filter(athlete_name == athleteName) %>% pull(p) %>% .[[1]]
            )
          )
        )
      }, error = function(e) {
        print(e)
      })
  
  
  
})))

x


```

# Report Glossary

### GPS Metric Overview

------------------------------------------------------------------------

**Total Distance** (TD)

-   Distance covered in meters (m)

**Total Intensive Distance** (TID)

-   General Definition - Distance covered when running at and above a moderate intensity, plus distance covered when accelerating and decelerating quickly
-   Technical Definition - Distance covered when metabolic power is greater than 25.5 watts per kilogram (m \> 25.5 W/kg)

**High Speed Running Distance** (HSRD)

-   General Definition - Distance covered when running distance covered when running at and above a moderate intensity,
-   Technical Definition Distance covered when running speed is greater than 5.5 meters per second (m \> 5.5 m/s)

**Acceleration / Deceleration Distance** (Ac/DcD)

-   General Definition - Distance covered when accelerating and decelerating quickly
-   Technical Definition - Distance covered when accelerating or decelerating greater than 25.5 watts per kilogram (m \> 25.5 W/kg)

**Sprint Distance** (SprD)

-   General Definition - Distance covered when sprinting approximately 80% of max speed
-   Technical Definition - Distance covered when running speed is greater than 7.0 meters per second (m \> 7 m/s)

**Acceleration Count** (Ac\#)

-   General Definition - Count of quick accelerations
-   Technical Definition - Count of events when acceleration is greater than 3 meters per second per second (count \> 3 m/s**²**)

**Deceleration Count** (Dc\#)

-   General Definition - Count of of quick deceleration
-   Technical Definition - Count of events when deceleration is greater than -3 meters per second per second (count \> -3 m/s**²**)
