---
title: "DTR"
output:
  flexdashboard::flex_dashboard:
    logo: USSF-Primary48.png
    vertical_layout: scroll
    orientation: rows
    css: mytheme.css
editor_options:
  chunk_output_type: console
params:
  campDateStart: '2022-03-21' 
  campDateEnd: '2022-03-31' 
  sessionDate: '2022-03-30'
  sessionMatchDay: 'MD vs Costa Rica'
  showGk: FALSE
  showSess: TRUE
    
---

```{r setup, include=FALSE}

  library(flexdashboard)
  library(tidyverse)
  library(dbplyr)
  library(plotly)
  library(MNTSportScience)
  library(readxl)
  library(lubridate)
  library(reactable)
  library(htmltools)
  library(glue)
  library(neon)
  library(RColorBrewer)
  library(crosstalk)
  
  #Statsports functions
  #I need to move these functions to the MNTSportScience Package
    source('TEMP.R')

  #General Dates - yyyy-mm-dd
    campDateStart <- params$campDateStart %>% as.Date()
    campDateEnd <- params$campDateEnd %>% as.Date()
    sessionDate <- params$sessionDate %>% as.Date()
    sessionMatchDay <- params$sessionMatchDay
    showGk <- params$showGk
    showSess <- params$showSess

  #Session Title
    pageTitle <- glue("DTR | {format(sessionDate,'%b-%d-%y')} | {sessionMatchDay}")
    
  #Connection to MYSQL in Amazon
    amzCon <- MNTSportScience::create_amz_mysql_con(dbName = "sandbox_jwebb")
  
  #Connection to sqlite
    # sqliteCon <- create_local_sqlite_con(dbName = "D:/statsports/statsports.sqlite")

    statsProfile <- pull_smartabase(
      type = 'profile',
      form = 'STATSports Profile',
      start_date = format(campDateStart, "%d/%m/%Y"),
      end_date   = format(campDateEnd, "%d/%m/%Y"), 
      filter_user_key = "group", 
      filter_user_value = "USMNT - Current"
    ) %>% select(about, name_display = `Display Name`)
    
    #Smartabase RPE 
    rpe <- pull_smartabase(
      form       = 'MNT RPE',
      start_date = format(campDateStart, "%d/%m/%Y"),
      end_date   = format(campDateEnd, "%d/%m/%Y"), 
      filter_user_key = "group", 
      filter_user_value = "USMNT - Current"
    ) %>% select(
      about,
      `Last Name`, 
      `First Name`,
      `Date` = start_date, 
      `RPE` = `RPE Score`,
      `AM/PM` = `Session Type`
    ) %>% mutate(
      Weekday = weekdays(dmy(Date)),
      Date = dmy(Date),
      `RPE Adjusted` = RPE / 2
    ) %>% 
    left_join(., statsProfile, by = 'about')

  #Get Score Inputs
    scoreInput <-  read_excel("C:/Users/jorda/Box/Analytics/Daily Training Report-USMNT (New).xlsx", 
      sheet = "Score Inputs", col_types = c("text", "text",
          "numeric", "numeric", "numeric", 
          "numeric", "numeric", "skip", "numeric", 
          "numeric", "numeric", "numeric", 
          "numeric", "numeric", "skip", "numeric", 
          "numeric", "numeric", "numeric", 
          "numeric", "numeric", "numeric", 
          "numeric", "numeric", "numeric"), 
      skip = 1) %>% rename(
      name_last = name_last,
      dist = `Distance Total`,
      dist_min = `Distance Per Minute`,
      mp_avg = `Avg Metabolic Loading Dist`,
      hml_dist = `High Metabolic Loading Dist`,
      vel_z6_dist = `Speed Zone 6`,
      hsr_dist = `High Speed Running`,
      si = `Speed Intensity`,
      hml_dist_min = `High Metabolic Loading Per Min`,
      hsr_dist_min = `High Speed Running Per Min`,
      si_min = `Speed Intensity Per Min`,
      exp_dist = `Explosive Dist`,
      dsl = `Dynamic Stress Load`,
      dsl_min = `Dynamic Stress Load Per Min`,
      acc_z36_cnt = `Accels Z3 - Z6`,
      acc_z46_cnt = `Accels Z4 - Z6`,
      dec_z36_cnt = `Decels Z3 - Z6`,
      dec_z46_cnt = `Decels Z4 - Z6`,
      hr_z6_dur = `Time in HR Zone 6`,
      hr_z56_dur = `Time in Red Zone`,
      hre  = `Heart Rate Exertion`,
      hre_min = `HRE Per Minute`
    ) %>% 
    rename_with(.fn = ~ paste0("score_", .x)) %>% 
    rename(name_last = score_name_last) %>% 
    mutate(
      x = name_last
    )
    
  shorten_athlete_status <- function(x){
    
    x[x == "Full"] <- "Full"
    x[x == "Full Limited Volume"] <- "Full Ltd Vol"
    x[x == "Limited"] <- "Ltd"
    x[x == "Reconditioning"] <- "Recon"
    x

  }
  
  make_drill_label <- function(drill_title, drill_type, drill_variation, drill_num, drill_int) {
    
    if (is.na(drill_type)) return(drill_title)
    
    if (drill_type == 'M') {
      x <- paste(drill_type, drill_variation, drill_int, collapse = ' - ')
    } else {
       x <- na.omit(c(drill_type, drill_variation, drill_num)) %>% as.vector() %>% paste(.,collapse = ' - ')
    }
  
    if (x == "") {
      x <- drill_title
    }
    
    x
    
  }
    
  ssDrill <- tbl(amzCon, "ssDrill") %>% 
    filter(drill_date >= campDateStart, drill_date <= campDateEnd) %>% 
    collect() %>% 
    mutate(position = convert_pos_num_to_name(position)) %>%
    rowwise() %>% 
    mutate(
      drill_label = make_drill_label(drill_title, drill_type, drill_variation, drill_num, drill_int),
      hsr_cnt = vel_z5_cnt, vel_z6_cnt,
      acc_cnt = acc_z4_cnt + acc_z5_cnt + acc_z6_cnt,
      dec_cnt = dec_z4_cnt + dec_z5_cnt + dec_z6_cnt,
      exp_dist = explosive_dist,
      exp_cnt = acc_cnt + dec_cnt
    ) %>% 
    ungroup() %>% 
    mutate(
      athlete_status = shorten_athlete_status(athlete_status)
    )

  metricNames <- c("dur",
      "dist", "dsl", "vel_max",
      "hml_dist", "hml_cnt", 
      "hsr_dist", "hsr_cnt",
      "vel_z5_dist", "vel_z6_dist", "vel_z5_cnt", "vel_z6_cnt",
      "exp_dist", "exp_cnt",
      "acc_cnt", "dec_cnt",
      "acc_z3_cnt", "acc_z4_cnt", "acc_z5_cnt", "acc_z6_cnt", 
      "dec_z3_cnt", "dec_z4_cnt", "dec_z5_cnt", "dec_z6_cnt", 
      "hre", "hr_z5_dur", "hr_z6_dur", "si",
      "impact_z3", "impact_z4", "impact_z5", "impact_z6",
      "impact_z36", "impact_z46", "impact_z56", "impact_z6"
    )
  

  ssSession <- ssDrill %>% 
    mutate(
      impact_z36 = impact_z3 + impact_z4 + impact_z5 + impact_z6,
      impact_z46 = impact_z4 + impact_z5 + impact_z6, 
      impact_z56 = impact_z5 + impact_z6, 
      impact_z6 = impact_z6
    ) %>% 
    select(
      drill_date, sess_type, session_title,
      drill_start_time, drill_end_time,
      name_display, position, athlete_status, name_first, name_last,
      dur,
      dist, dsl,
      hml_dist, hml_cnt, 
      hsr_dist, hsr_cnt,
      vel_z5_dist, vel_z6_dist, vel_z5_cnt, vel_z6_cnt,
      exp_dist, exp_cnt,
      acc_cnt, dec_cnt,
      acc_z3_cnt, acc_z4_cnt, acc_z5_cnt, acc_z6_cnt, 
      dec_z3_cnt, dec_z4_cnt, dec_z5_cnt, dec_z6_cnt, 
      hre, hr_z5_dur, hr_z6_dur,
      mp_avg, si, vel_max,
      impact_z3, impact_z4, impact_z5, impact_z6,
      impact_z36, impact_z46, impact_z56, impact_z6
    ) %>% 
    mutate(
      hre = ifelse(hre == 0, NA, hre),
      hr_z5_dur = ifelse(hre == 0, NA, hr_z5_dur),
      hr_z6_dur = ifelse(hre == 0, NA, hr_z5_dur)
    ) %>% 
    group_by(drill_date, sess_type, session_title, name_display, position, athlete_status) %>%
    summarise(.groups = 'keep', 
      mp_avg = {
        mp1 <- mp_avg * dur 
        mp2 <- sum(mp1)
        dur1 <- sum(dur)
        mp2 / dur1
      },
      vel_max = max(vel_max),
      across(all_of(metricNames), sum),
      session_start_time = sort(drill_start_time, decreasing = F) %>% .[1],
      session_end_time = sort(drill_end_time, decreasing = T) %>% .[1]
    ) %>%
    ungroup() %>% 
    rename(dur_drill = dur) %>% 
    mutate(
      dur_session = (strptime(session_end_time, "%H:%M:%OS") - strptime(session_start_time, "%H:%M:%OS")) %>% as.numeric() ,
      hr_z56_dur = hr_z5_dur + hr_z6_dur
    ) %>% 
    mutate(
      name_last = str_replace(name_display, ' ', replacement = "_") %>% str_split(., "_", simplify = T) %>% .[,2]
    ) %>% 
    left_join(x = ., y = scoreInput, by = c("name_display" = "score_name_display")) %>% 
    mutate(
      extensive_score = calc_extensive_score(
        dist = dist, 
        dist_game = score_dist, 
        dur = dur_drill, 
        dist_min_game = score_dist_min,
        mp_avg = mp_avg,
        mp_avg_game = score_mp_avg,
        hml_dist = hml_dist,
        hml_dist_game = score_hml_dist
      ),
      extensive_load = calc_load_scale(extensive_score),
      speed_score = calc_speed_score(
        dur = dur_drill, 
        vel_z5_dist = vel_z5_dist, 
        vel_z6_dist = vel_z6_dist, 
        hml_dist = hml_dist, 
        si = si, 
        vel_z6_dist_game = score_vel_z6_dist, 
        hml_dist_game = score_hml_dist, 
        vel_z56_dist_game = score_hsr_dist, 
        si_game = score_si, 
        hml_dist_min_game = score_hml_dist_min, 
        vel_z56_dist_min_game = score_hsr_dist_min, 
        si_min_game = score_si_min
      ),
      speed_load = calc_load_scale(speed_score),
      muscle_score = calc_muscle_score(
        dur = dur_drill,
        explosive_dist = exp_dist,
        hml_dist = hml_dist,
        dsl = dsl,
        acc_z3_cnt = acc_z3_cnt,
        acc_z4_cnt = acc_z4_cnt,
        acc_z5_cnt = acc_z5_cnt,
        acc_z6_cnt = acc_z6_cnt,
        dec_z3_cnt = dec_z3_cnt,
        dec_z4_cnt = dec_z4_cnt,
        dec_z5_cnt = dec_z5_cnt,
        dec_z6_cnt = dec_z6_cnt,
        explosive_dist_game = score_exp_dist,
        hml_dist_min_game = score_hml_dist_min,
        dsl_game = score_dsl,
        dsl_min_game = score_dsl_min,
        acc_z3456_cnt_game = score_acc_z36_cnt,
        acc_z456_cnt_game = score_acc_z46_cnt,
        dec_z3456_cnt_game = score_dec_z36_cnt,
        dec_z456_cnt_game = score_dec_z46_cnt
      ),
      muscle_load = calc_load_scale(muscle_score),
      cv_score = calc_cv_score(
        dur = dur_drill,
        hre = hre,
        hr_z5_dur = hr_z5_dur,
        hr_z6_dur = hr_z6_dur,
        hre_game = score_hre,
        hre_min_game = score_hre_min,
        hr_z56_dur_game = score_hr_z56_dur,
        hr_z6_dur_game = score_hr_z6_dur
      ),
      cv_load = calc_load_scale(cv_score)
    ) %>%
    mutate(
      total_score = calc_total_score(extensive_score, speed_score, muscle_score, cv_score),
      total_load = calc_load_scale(total_score),
      drill_date = as.Date(drill_date)
    ) %>% 
   left_join(., rpe, by = c("name_display" = "name_display", "drill_date" = "Date"))


```

---
title: `r pageTitle`
---


Daily Training Report {data-orientation=column}
=====================================

```{r, include=FALSE}

  #This section sets up data for the Daily Training Report 

  #Render a barchart for formattable
  bar_chart <- function(label, width = "100%", height = "12px", fill = "#00bfc4", background = NULL) {
    bar <- div(style = list(background = fill, width = width, height = height))
    chart <- div(style = list(flexGrow = 1, marginLeft = "6px", background = background), bar)
    div(style = list(display = "flex", alignItems = "center"), label, chart)
  }

  load_score_color_picker <- function(value){
    
      if (is.na(value)) return(NA)
    
      if (value >= 5) {
        "rgb(215,25,28)" 
      } else if (value >= 4) {
        "rgb(253,174,97)"
      } else if (value >= 3) {
        "rgb(255,255,191)" 
      } else if (value >= 2) {
        "rgb(166,217,106)" 
      } else if (value >= 1) {
        "rgb(26,150,65)" 
      } else {
        NA
      }
  
  }

  ssDTR <- ssSession %>% 
    filter(position != 'GK') %>%
    filter(drill_date == sessionDate) %>% 
    rename(dur = dur_drill) %>% 
    mutate(
      name_display = glue("{name_last.x}, {substr(name_display, 1, 1)}"),
      # name_display = str_replace(name_display, ' ', replacement = "_") %>% str_split(., "_", simplify = T) %>% .[,2]
      acc_dec_cnt = acc_cnt + dec_cnt,
      hml_dist = round(hml_dist,0),
      dist_min = round(dist / dur,0),
      dsl = round(dsl,0),
      dur = round(dur,0),
      hr_z56_dur = round(hr_z56_dur, 0),
      hr_z6_dur = round(hr_z6_dur, 0),
      hre = round(hre,0),
      rpe = `RPE Adjusted`,
      vel_max = round(vel_max, 1)
    ) %>% 
    select(
      position,
      name_display, 
      athlete_status,
      dur, 
      vel_max,
      dist, 
      dist_min,
      extensive_load,
      hml_dist,
      hsr_dist,
      vel_z6_dist,
      speed_load,
      exp_dist,
      acc_cnt,
      dec_cnt,
      dsl,
      muscle_load,
      hr_z56_dur,
      hr_z6_dur,
      hre,
      cv_load,
      total_load,
      rpe, 
      acc_cnt
    )
  
  FB_height <- ssDTR %>% filter(position == 'FB') %>% pull(name_display) %>% unique() %>% length() %>% {. * 30 + 142}
  CB_height <- ssDTR %>% filter(position == 'CB') %>% pull(name_display) %>% unique() %>% length()  %>% {. * 30 + 142}
  CM_height <- ssDTR %>% filter(position == 'CM') %>% pull(name_display) %>% unique() %>% length() %>% {. * 30 + 142}
  AM_height <- ssDTR %>% filter(position == 'AM') %>% pull(name_display) %>% unique() %>% length()  %>% {. * 30 + 142}
  WAM_height <- ssDTR %>% filter(position == 'WAM') %>% pull(name_display) %>% unique() %>% length()  %>% {. * 30 + 142}
  FWD_height <- ssDTR %>% filter(position == 'FWD') %>% pull(name_display) %>% unique() %>% length() %>% {. * 30 + 142}
  Full_height <- ssDTR %>% filter(athlete_status == 'Full') %>% pull(name_display) %>% unique() %>% length() %>% {. * 30 + 142}
  Not_full_height <- ssDTR %>% filter(athlete_status != 'Full') %>% pull(name_display) %>%  unique() %>% length() %>% {. * 30 + 142}
  
  js_header <- function(subLabel) {
    JS(paste0("function(colInfo) {return colInfo.column.name + '<div style=\"color: #999; font-size: 10px\">",subLabel,"</div>'}"))
  }
  
create_DTR_reacttable <- function(x, positionName) { 
  
  fill <- "#18233F"
  color <- "#fff" 
  
  x %>% 
    reactable(
      data = .,
      compact = T,
      pagination = F,
      bordered = T,
      defaultColDef = colDef( 
        cell = function(value, index, name) {
          
          if (is.na(value)){
            width <- "0%"
            padMax <- c(x[[name]], "NA") %>% nchar() %>% max(., na.rm = TRUE)
            value <- format(value, width = padMax, justify = "right")
            bar_chart(value, width = width, fill = fill, background = "#FFFFFF")
          } else if (value == 0) {
            width <- "0%"
            padMax <- c(x[[name]], "NA") %>% nchar() %>% max(., na.rm = TRUE)
            value <- format(value, width = padMax, justify = "right")
            bar_chart(value, width = width, fill = fill, background = "#e1e1e1")
          } else {
            width <- paste0(value / max(x[[name]], na.rm = TRUE) * 100, "%")
            padMax <- x[[name]] %>% nchar() %>% max(., na.rm = TRUE)
            value <- format(value, width = padMax, justify = "right")
            bar_chart(value, width = width, fill = fill, background = "#e1e1e1")
          }
          
        },
        footer = function(values, name) {  

          value <- mean(values, na.rm = TRUE) %>% round(.,0) 

          if (is.nan(value)) {
            width <- "0%"
            padMax <- c(x[[name]], "NA") %>% nchar() %>% max(., na.rm = TRUE)
            value <- format("NA", width = padMax, justify = "right")
            bar_chart(value, width = width, fill = fill, background =  "#FFFFFF")
          } else if (0 == value) {
            width <- "0%"
            padMax <- c(x[[name]], "NA") %>% nchar() %>% max(., na.rm = TRUE)
            value <- format(value, width = padMax, justify = "right")
            bar_chart(value, width = width, fill = fill, background = "#e1e1e1")
          } else {
            width <- paste0(value / max(values, na.rm = T) * 100, "%")
            padMax <- values %>% nchar() %>% max(., na.rm = TRUE)
            value <- format(value, width = padMax, justify = "right")
            bar_chart(value, width = width, fill = fill, background = "#e1e1e1")
          }
          
        },
        headerStyle = list(
          fontWeight = 700, 
          fontSize = 12, 
          textAlign = "left"
        ),
        style = list(
          fontFamily = "monospace", 
          fontWeight = 400, 
          fontSize = 14, 
          color = 'black', 
          whiteSpace = "pre", 
          borderRight = "1px solid rgba(0, 0, 0, 0.1)"
        ),
        footerStyle = list(
          fontFamily = "monospace", 
          fontWeight = 700, 
          fontSize = 14, 
          color = 'black', 
          whiteSpace = "pre", 
          borderRight = "1px solid rgba(0, 0, 0, 0.1)"
        ),
        format = colFormat(digits = 0),
        html = T
      ),
      columns = list(
        name_display = colDef( 
          name = positionName,
          minWidth = 110,
          cell = function(value) value,
          align = 'left',
          footer = glue("Average:"),
          style = list(fontFamily = 'Arial', fontSize = 12)
        ),
        athlete_status = colDef(
          name = "Status",
          minWidth = 100,
          cell = function(value) value,
          align = 'left',
          footer = "",
          style = list(fontFamily = 'Arial', fontSize = 12)
        ),
        dur = colDef(
          name = "Working Time", 
          align = 'center',
          header = js_header("(min)"),
          minWidth = 60,
          cell = function(value) value,
          footer = function(values) mean(values) %>% round(.,0)
        ),
        vel_max = colDef(
          name = "Max Speed", 
          header = js_header("(m/s)"),
          align = 'left',
          minWidth = 80
        ),
        dist = colDef(
          name = "   Total Distance   ", 
          header = js_header("(m)"),
          align = 'left',
          minWidth = 80
        ),
        dist_min = colDef(
          name = "Dist Per Min", 
          header = js_header("(m/min)"),
          align = 'left',
          minWidth = 80
        ),
        extensive_load = colDef(
          name = "Ext Load", 
          header = js_header("(au)"),
          cell = function(value){div(class = "roundcorners", style = list(background = load_score_color_picker(value)), value)},
          footer = function(values){
            value <- mean(values) %>% round(.,0)
            div(class = "roundcorners", style = list(background = load_score_color_picker(value)), value)
          },
          align = 'center',
          width = 55
        ),
        hml_dist = colDef(
          name = "Intensive Dist", 
          header = js_header("(m > 25.5 w/kg)"),
          align = 'left',
          minWidth = 80
        ),
        hsr_dist = colDef(
          name = "High Int Dist", 
          header = js_header("(m > 5.5 m/s)"),
          align = 'left',
          minWidth = 80
        ),
        vel_z6_dist = colDef(
          name = "Sprint Dist", 
          header = js_header("(m > 7.0 m/s)"),
          align = 'left',
          minWidth = 80
        ),
        speed_load = colDef(
          name = "Speed Load", 
          header = js_header("(au)"),
          cell = function(value){div(class = "roundcorners", style = list(background = load_score_color_picker(value)), value)},
          footer = function(values){
            value <- mean(values) %>% round(.,0)
            div(class = "roundcorners", style = list(background = load_score_color_picker(value)), value)
          },
          align = 'center',
          width = 55
        ),
        exp_dist = colDef(
          name = "Acc/Dec Dist", 
          header = js_header("(m > ±3 m/s²)"),
          align = 'left',
          minWidth = 80
        ),
        acc_cnt = colDef(
          name = "Acc Count", 
          header = js_header("(# > +3 m/s²)"),
          align = 'left',
          minWidth = 80
        ),
        dec_cnt = colDef(
          name = "Dec Count", 
          header = js_header("(# < -3 m/s²)"),
          align = 'left',
          minWidth = 80
        ),
        dsl = colDef(
          name = "Muscle Stress", 
          header = js_header("(au)"),
          align = 'left',
          minWidth = 80
        ),
        muscle_load = colDef(
          name = "Muscle Load", 
          header = js_header("(au)"),
          cell = function(value){div(class = "roundcorners", style = list(background = load_score_color_picker(value)), value)},
          footer = function(values){
            value <- mean(values) %>% round(.,0)
            div(class = "roundcorners", style = list(background = load_score_color_picker(value)), value)
          },
          align = 'center',
          width = 55
        ),
        hr_z56_dur = colDef(
          name = "Time HR >AT", 
          header = js_header("(min)"),
          align = 'left',
          width = 80
        ),
        hr_z6_dur = colDef(
          name = "Time HR >90%", 
          header = js_header("(min)"),
          align = 'left',
          width = 80
        ),
        hre = colDef(
          name = "HR Exertion", 
          header = js_header("(au)"),
          align = 'left',
          width = 80
        ),
        cv_load = colDef(
          name = "CV Load", 
          header = js_header("(au)"),
          cell = function(value){div(class = "roundcorners", style = list(background = load_score_color_picker(value)), value)},
          footer = function(values){
            value <- mean(values, na.rm = T) %>% round(.,0)
            div(class = "roundcorners", style = list(background = load_score_color_picker(value)), value)
          },
          align = 'center',
          width = 55
        ),
        total_load = colDef(
          name = "Total Load", 
          header = js_header("(au)"),
          cell = function(value){div(class = "roundcorners", style = list(background = load_score_color_picker(value)), value)},
          footer = function(values){
            value <- mean(values, na.rm = T) %>% round(.,0)
            div(class = "roundcorners", style = list(background = load_score_color_picker(value)), value)
          },
          align = 'center',
          width = 55
        ),
        rpe = colDef(
          name = "RPE Load", 
          header = js_header("(au)"),
          cell = function(value){div(class = "roundcorners", style = list(background = load_score_color_picker(value)), value)},
          footer = function(values){
            value <- mean(values) %>% round(.,0)
            div(class = "roundcorners", style = list(background = load_score_color_picker(value)), value)
          },
          align = 'center',
          width = 55
        )
      ),
      columnGroups = list(
        colGroup(name = "Extensive Metrics", columns = c("dist", "dist_min", "extensive_load")),
        colGroup(name = "Speed Metrics", columns = c("hml_dist", "hsr_dist", "vel_z6_dist", "speed_load")),
        colGroup(name = "Muscle Metrics", columns = c("exp_dist", "dsl", "acc_cnt", "dec_cnt", "muscle_load")),
        colGroup(name = "Cardiovascular Metrics", columns = c("hr_z56_dur", "hr_z6_dur", "hre", "cv_load"))
      )
    )
}

```

```{css, echo=FALSE}

  .roundcorners {
      text-align: center;
      border-radius: 8px;
      color: #000;
      padding: 2px;
      width: 45px;
      height: 20px;
    }


```

row {data-height=`r FB_height`}
-------------------------------------

### Full Back

```{r DTR FB, message=FALSE, warning=FALSE}

  ssDTR %>% 
    filter(position == "FB") %>% 
    select(-position) %>% 
    create_DTR_reacttable(., "Full Back")

```

row {data-height=`r CB_height`}
-------------------------------------

### Center Back

```{r DTR CB, message=FALSE, warning=FALSE}

  ssDTR %>% 
    filter(position == "CB") %>% 
    select(-position) %>% 
    create_DTR_reacttable(., "Center Back")

```

row {data-height=`r CM_height`}
-------------------------------------

### Center Midfield
```{r DTR CM, message=FALSE, warning=FALSE}

  ssDTR %>% 
    filter(position == "CM") %>% 
    select(-position) %>% 
    create_DTR_reacttable(., "Center Midfield")

```

row {data-height=`r AM_height`}
-------------------------------------

### Attacking Midfield

```{r DTR AM, message=FALSE, warning=FALSE}

  ssDTR %>% 
    filter(position == "AM") %>% 
    select(-position) %>% 
    create_DTR_reacttable(., "Attacking Midfield")

```

row {data-height=`r WAM_height`}
-------------------------------------

### Wide Attacking Midfield

```{r DTR WAM, message=FALSE, warning=FALSE}

  ssDTR %>% 
    filter(position == "WAM") %>% 
    select(-position) %>% 
    create_DTR_reacttable(., "Wide Attacking Midfield")

```

row {data-height=`r FWD_height`}
-------------------------------------

### Forward

```{r DTR FWD, message=FALSE, warning=FALSE}

  ssDTR %>% 
    filter(position == "FWD") %>% 
    select(-position) %>% 
    create_DTR_reacttable(., "Forward")

```

row {data-height=`r Full_height`}
-------------------------------------

### Full

```{r DTR Team Full, message=FALSE, warning=FALSE}

  ssDTR %>% 
    filter(athlete_status == 'Full') %>% 
    select(-position) %>% 
    create_DTR_reacttable(., "Team Full")

```

row {data-height=`r Not_full_height`}
-------------------------------------

### Team Not Full


```{r DTR Team Limited, message=FALSE, warning=FALSE}

  ssDTR %>% 
    filter(athlete_status != 'Full') %>% 
    select(-position) %>% 
    create_DTR_reacttable(., "Team Not Full")

```

Session Overview
=====================================

```{r, include=FALSE}

    getColorPallete <- colorRampPalette(brewer.pal(12, "Set3"))

    drillColors <- ssDrill %>% 
      ungroup() %>% 
      filter(drill_date == sessionDate) %>% 
      filter(drill_label != "") %>%
      select(drill_label, drill_status) %>% 
      unique() %>% 
      mutate(drill_color = getColorPallete(n())) %>%
      filter(drill_status == "include") %>% 
      select(drill_label, drill_color)

```

Row {data-height="175"}
-------------------------------------

### Duration Intensity Overview

```{r eval=showSess, include=showSess}

# Create Drill Start Time -------------------------------------------------

  timeChartData <- ssDrill %>% 
    filter(athlete_status == 'Full') %>% 
    filter(!is.na(drill_type)) %>%
    filter(position != 'GK') %>% 
    filter(drill_date == sessionDate) %>%
    filter(drill_status == "include") %>%
    select(
      session_title,
      dist,
      dur,
      drill_date, 
      drill_label,
      drill_title,
      drill_type, 
      drill_variation,
      drill_num,
      drill_start_time, 
      drill_end_time
    ) %>% 
    mutate(dist_min = dist / dur) %>% 
    group_by(session_title, drill_date, drill_title, drill_label) %>% 
    mutate(
      drill_start_time = strptime(drill_start_time, "%H:%M:%OS"),
      drill_end_time = strptime(drill_end_time, "%H:%M:%OS")
    ) %>% 
    summarise(.groups = 'keep',
      dist_min = mean(dist_min, na.rm = T),
      drill_start_time = drill_start_time %>% sort(decreasing = F) %>% .[1],
      drill_end_time = drill_end_time %>% sort(decreasing = T) %>% .[1]
    ) %>% 
    ungroup() %>% 
    arrange(drill_start_time) %>% 
    mutate(
      drill_label = factor(drill_label, levels = unique(drill_label))
    ) 

  gg <- timeChartData %>% 
    ggplot() +
      geom_rect(aes(
        xmin = drill_start_time, 
        xmax = drill_end_time, 
        ymin = 0, 
        ymax = dist_min, 
        fill = drill_label,
        group = drill_label
      )) + 
      ylab("m / min") +
      theme(
        axis.text=element_text(size=6),
        legend.position='none'
      ) +
      scale_fill_manual(values = drillColors$drill_color)
      
  
  ggplotly(gg)
  


```

### Active / Passive Time

```{R eval=showSess, include=showSess}

#Session Total Time
x <- ssDrill %>% 
  filter(
    drill_date == sessionDate,
    position != 'GK',
    athlete_status == 'Full',
    # !is.na(drill_type),
    drill_status == 'include'
  ) %>%
  select(
    session_title,
    drill_date, 
    drill_title,
    drill_start_time, 
    drill_end_time,
    session_start_time,
    session_end_time
  ) %>% 
  mutate(
    drill_start_time = strptime(drill_start_time, "%H:%M:%OS"),
    drill_end_time = strptime(drill_end_time, "%H:%M:%OS"),
  ) %>% 
  group_by(session_title, drill_date, drill_title) %>% 
  summarise(.groups = 'keep',
    drill_start_time = min(drill_start_time),
    drill_end_time = max(drill_end_time),
  ) %>% 
  ungroup() %>% 
  mutate(
    session_start_time = min(drill_start_time),
    session_end_time = max(drill_end_time),
    drill_time = difftime(drill_end_time, drill_start_time, units = "mins") %>% as.numeric(), 
    session_time = difftime(session_end_time, session_start_time, units = "mins") %>% as.numeric()
  ) %>% 
  group_by(session_title, drill_date) %>% 
  summarise(.groups = 'keep',
    activeTimeMin = sum(drill_time),
    totalTimeMin = min(session_time)
  ) %>% 
  ungroup() %>% 
  mutate(
    inactiveTimeMin = totalTimeMin - activeTimeMin,
    activeTimePct = (activeTimeMin / totalTimeMin) * 100
  )

gg <- x %>% 
  select(session_title, inactiveTimeMin, activeTimeMin) %>% 
  rename(`Working Time` = activeTimeMin, `Non-Working Time` = inactiveTimeMin) %>% 
  pivot_longer(cols = c(`Working Time`, `Non-Working Time`)) %>% 
  mutate(label =  glue("{round(value,0)} min \n {name}")) %>% 
  ggplot(aes(x = round(value,0), y = session_title, fill = name, label = label)) + 
    geom_col(position = 'stack') +
    geom_text(position = position_stack(vjust = .5), size = 3) +
    theme(
      axis.title.y=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks.y=element_blank()
    ) +
    xlab("Duration Minutes") +
    theme(
      axis.text=element_text(size=4),
      legend.position='none'
    ) +
    scale_color_brewer(palette = "Dark2")

    
  ggplotly(gg) 


```

Row
-------------------------------------

### Metric Breakdown

```{r echo=FALSE, fig.height=8}

mNames <- c("Working Time", "Total Dist","Intensive Dist", "High Int Dist", "Explosive Dist", "Sprint Dist", "Acc Count", "Dec Count")

ssDrill2 <- ssDrill %>%
  filter(position != 'GK') %>%
  # filter(!is.na(drill_type)) %>%
  filter(drill_status == 'include') %>%
  filter(session_date == sessionDate) %>%
  filter(athlete_status == 'Full') %>%
  mutate(
    drill_name_short = factor(drill_name_short, levels =
                                ssDrill %>% filter(session_date == sessionDate) %>%
                                arrange(drill_start_time) %>%
                                pull(drill_name_short) %>%
                                unique()
    ),
    acc_dec_cnt = acc_cnt + dec_cnt
  ) %>%
  rename(
    `Working Time` = dur,
    `Total Dist` = dist,
    `Intensive Dist` = hml_dist,
    `High Int Dist` = hsr_dist,
    `Explosive Dist` = exp_dist,
    `Sprint Dist` = vel_z6_dist,
    `Acc Count` = acc_cnt,
    `Dec Count` = dec_cnt
  ) %>%
  select(session_date, session_title, name_display, drill_name_short, drill_start_time, drill_end_time, all_of(mNames)) %>% 
  pivot_longer(cols = all_of(mNames), names_to = 'metric') %>%
  mutate(metric = factor(metric, levels = mNames)) %>%
  group_by(session_date, session_title, name_display, drill_name_short, metric) %>% 
  summarise(.groups = 'keep', 
    value = sum(value),
    drill_start_time = min(drill_start_time),
    drill_end_time = max(drill_end_time),
  ) %>% 
  group_by(session_date, session_title, drill_name_short, metric) %>% 
  summarise(.groups = 'keep', 
    ci = list(mean_cl_boot(value)),
    drill_start_time = min(drill_start_time),
    drill_end_time = max(drill_end_time)
  ) %>%
  unnest(ci) %>%
  rename(mean=y, lwr=ymin, upr=ymax)

ssTeam <- ssDrill2 %>%
  group_by(session_date, session_title, metric) %>%
  summarise(.groups = 'keep',
            mean = sum(mean),
            lwr = sum(lwr),
            upr = sum(upr)
  ) %>%
  rowwise() %>%
  mutate(target = runif(1, min = mean * .75, mean * 1.25) %>% round(., 1)) %>%
  ungroup()

make_plot <- function(data, drillColors) {
  
  showLegend <- data$showLegend %>% unique()
  
  data %>%
    arrange(drill_name_short) %>%
    plot_ly(
      data = ., x = ~mean, y = ~metric,
      color = ~factor(drill_name_short),
      colors = drillColors,
      legendgroup = ~drill_name_short
    ) %>%
    add_trace(type="bar", legendgroup = ~drill_name_short,  showlegend = showLegend) %>%
    layout(barmode = "stack")
  
}

x <- ssDrill2 %>%
  mutate(
    showLegend = ifelse(metric == ssDrill2$metric %>% unique() %>% .[1], T, F)
  ) %>%
  group_by(metric) %>%
  group_split() %>%
  map(.x = ., .f = ~make_plot(.x, drillColors$drill_color))


x %>% subplot(., nrows = 8, shareX = FALSE, shareY = FALSE)


```

Camp Overview
=====================================

row {data-height=2400}
-------------------------------------

### Team Average Overview

```{r echo=FALSE, message=FALSE, warning=FALSE}

  #Create Plotly Of Camp

  mNames <- c("Working Time", "Total Dist","Intensive Dist", "High Int Dist", "Explosive Dist", "Sprint Dist", "Acc Dec Count")

 ssTeam <- ssSession %>% 
    filter(athlete_status == 'Full') %>% 
    filter(position != 'GK') %>% 
    mutate(acc_dec_cnt = acc_cnt + dec_cnt) %>% 
    rename(
      `Working Time` = dur_drill,
      `Total Dist` = dist,
      `Intensive Dist` = hml_dist,
      `High Int Dist` = hsr_dist,
      `Explosive Dist` = exp_dist,
      `Sprint Dist` = vel_z6_dist,
      `Acc Dec Count` = acc_dec_cnt
    ) %>% 
    select(drill_date, sess_type, session_title, all_of(mNames)) %>%
    pivot_longer(cols = all_of(mNames), names_to = 'metric') %>% 
    mutate(metric = factor(metric, levels = mNames)) %>% 
    group_by(drill_date, sess_type, session_title, metric) %>% 
    summarise(.groups = 'keep',
      ci = list(mean_cl_boot(value))
    ) %>%
    unnest(ci) %>% 
    rename(mean=y, lwr=ymin, upr=ymax) 

  p <- ssTeam %>% 
    group_by(metric) %>% 
    group_split() %>% 
    map(.x = ., .f = function(.x){
      
      yTitle <- .x$metric %>% unique() 

      .x %>% 
        plot_ly() %>% 
        add_trace(
            x = ~drill_date, 
            y = ~round(mean,0),
            marker = list(color = '#18233F'),
            type = "bar",
            showlegend = F,
            hovertext = ~glue("
              Metric: {metric}
              Type: {sess_type}
            "),
            error_y = list(
              type = "data",
              array = ~c(round(lwr-mean,1),round(upr-mean,1)),
              color = "grey"
            )
          ) %>% 
          layout(
            yaxis = list(title = yTitle),
            xaxis = list(title = "")
          ) %>%
          layout(width = 700)
        
    })
   
   subplot(p, nrows = length(p), shareY = F, titleY = T)

  
```

GK Daily Training Report
=====================================

row 
-------------------------------------

### GK Average Overview

```{r eval=showGk, message=FALSE, warning=FALSE, include=showGk}

  create_dtr_gk_reacttable <- function(x) { 
    
    positionName <- "Goal Keeper"
    
    fill <- "#18233F"
    color <- "#fff" 
  
    x %>% 
      select(-position) %>% 
      reactable(
        data = .,
        compact = T,
        pagination = F,
        bordered = T,
        defaultColDef = colDef(
          cell = function(value, index, name) {
            width <- paste0(value / max(x[[name]]) * 100, "%")
            padMax <- x[[name]] %>% nchar() %>% max()
            value <- format(value, width = padMax, justify = "right")
            bar_chart(value, width = width, fill = fill, background = "#e1e1e1")
          },
          footer = function(values, name) {
            value <- mean(values) %>% round(.,0)
            width <- paste0(value / max(values) * 100, "%")
            padMax <- values %>% nchar() %>% max()
            value <- format(value, width = padMax, justify = "right")
            bar_chart(value, width = width, fill = fill, background = "#e1e1e1")
          },
          headerStyle = list(
            fontWeight = 700,
            fontSize = 12,
            textAlign = "left"
          ),
          style = list(
            fontFamily = "monospace",
            fontWeight = 400,
            fontSize = 14,
            color = 'black',
            whiteSpace = "pre",
            borderRight = "1px solid rgba(0, 0, 0, 0.1)"
          ),
          footerStyle = list(
            fontFamily = "monospace",
            fontWeight = 700,
            fontSize = 14,
            color = 'black',
            whiteSpace = "pre",
            borderRight = "1px solid rgba(0, 0, 0, 0.1)"
          ),
          format = colFormat(digits = 0),
          html = T
        ),
        columns = list(
          name_display = colDef( 
            name = positionName,
            minWidth = 100,
            cell = function(value) value,
            align = 'left',
            footer = glue("Average:"),
            style = list(fontFamily = 'Arial', fontSize = 12)
          ),
          dur = colDef(
            name = "Working Time",
            align = 'center',
            header = js_header("(min)"),
            minWidth = 60,
            cell = function(value) value,
            footer = function(values) mean(values) %>% round(.,0)
          ),
          dist = colDef(
            name = "   Total Distance   ",
            header = js_header("(m)"),
            align = 'left',
            minWidth = 85
          ),
          vel_max = colDef(
            name = "Max Speed",
            header = js_header("(m/s)"),
            align = 'left',
            minWidth = 85
          ),
          hml_dist = colDef(
            name = "Intensive Dist",
            header = js_header("(m > 25.5 w/kg)"),
            align = 'left',
            minWidth = 85
          ),
          hsr_dist = colDef(
            name = "High Int Dist",
            header = js_header("(m > 5.5 m/s)"),
            align = 'left',
            minWidth = 85
          ),
          vel_z6_dist = colDef(
            name = "Sprint Dist",
            header = js_header("(m > 7.0 m/s)"),
            align = 'left',
            minWidth = 85
          ),
          exp_dist = colDef(
            name = "Acc/Dec Dist",
            header = js_header("(m > ±3 m/s²)"),
            align = 'left',
            minWidth = 85
          ),
          speed_load = colDef(
            name = "Speed Load",
            header = js_header("(au)"),
            cell = function(value){div(class = "roundcorners", style = list(background = load_score_color_picker(value)), value)},
            footer = function(values){
              value <- mean(values) %>% round(.,0)
              div(class = "roundcorners", style = list(background = load_score_color_picker(value)), value)
            },
            align = 'center',
            width = 55
          ),
          dsl = colDef(
            name = "Muscle Stress",
            header = js_header("(au)"),
            align = 'left',
            minWidth = 85
          ),
          muscle_load = colDef(
            name = "Muscle Load",
            header = js_header("(au)"),
            cell = function(value){div(class = "roundcorners", style = list(background = load_score_color_picker(value)), value)},
            footer = function(values){
              value <- mean(values) %>% round(.,0)
              div(class = "roundcorners", style = list(background = load_score_color_picker(value)), value)
            },
            align = 'center',
            width = 55
          ),
          impact_z46 = colDef(
            name = "Impacts 4-6",
            header = js_header("(au)"),
            align = 'left',
            minWidth = 85
          ),
          impact_z56 = colDef(
            name = "Impacts 5-6",
            header = js_header("(au)"),
            align = 'left',
            minWidth = 85
          ),
          impact_z6 = colDef(
            name = "Impacts 6",
            header = js_header("(au)"),
            align = 'left',
            minWidth = 85
          ),
          impact_stress = colDef(
            name = "Impact Load",
            header = js_header("(au)"),
            cell = function(value){div(class = "roundcorners", style = list(background = load_score_color_picker(value)), value)},
            footer = function(values){
              value <- mean(values) %>% round(.,0)
              div(class = "roundcorners", style = list(background = load_score_color_picker(value)), value)
            },
            align = 'center',
            width = 55
          ),
          impact_load = colDef(
            name = "Impact Load",
            header = js_header("(au)"),
            cell = function(value){div(class = "roundcorners", style = list(background = load_score_color_picker(value)), value)},
            footer = function(values){
              value <- mean(values) %>% round(.,0)
              div(class = "roundcorners", style = list(background = load_score_color_picker(value)), value)
            },
            align = 'center',
            width = 55
          ),
          total_load = colDef(
            name = "Total Load",
            header = js_header("(au)"),
            cell = function(value){div(class = "roundcorners", style = list(background = load_score_color_picker(value)), value)},
            footer = function(values){
              value <- mean(values) %>% round(.,0)
              div(class = "roundcorners", style = list(background = load_score_color_picker(value)), value)
            },
            align = 'center',
            width = 55
          ),
          rpe = colDef(
            name = "RPE Load",
            header = js_header("(au)"),
            cell = function(value){div(class = "roundcorners", style = list(background = load_score_color_picker(value)), value)},
            footer = function(values){
              value <- mean(values) %>% round(.,0)
              div(class = "roundcorners", style = list(background = load_score_color_picker(value)), value)
            },
            align = 'center',
            width = 55
          )
        ),
        columnGroups = list(
          colGroup(name = "Speed Metrics", columns = c("vel_max", "dist", "hsr_dist", "vel_z6_dist", "hml_dist", "exp_dist", "speed_load")),
          colGroup(name = "Muscle Metrics", columns = c("dsl", "muscle_load")),
          colGroup(name = "Impact Metrics", columns = c("impact_z46", "impact_z56", "impact_z6", "impact_load"))
        )
      )
}

  mNames <- c(
    "dur_drill", 
    "vel_max",
    "dist",
    "hsr_dist", 
    "vel_z6_dist", 
    "hml_dist", 
    "exp_dist", 
    "dsl",
    "impact_z46",
    "impact_z56",
    "impact_z6"
  )
  
  ssGoalKeeper <- ssSession %>% 
    filter(position == 'GK') %>% 
    filter(drill_date == sessionDate) %>% 
    rename(dur = dur_drill) %>% 
    mutate(
      name_display = str_replace(name_display, ' ', replacement = "_") %>% str_split(., "_", simplify = T) %>% .[,2],
      acc_dec_cnt = acc_cnt + dec_cnt,
      hml_dist = round(hml_dist,0),
      dist_min = round(dist / dur,0),
      dsl = round(dsl,0),
      dur = round(dur,0),
      rpe = `RPE Adjusted`, 
      speed_score = calc_gk_speed_score(dur = dur, si = si, vel_z5_dist = vel_z5_dist, vel_z6_dist = vel_z6_dist, mp_avg = mp_avg, exp_dist = exp_dist),
      speed_load = calc_load_scale(speed_score),
      muscle_score = calc_gk_muscle_score(dur = dur, exp_dist = exp_dist, dsl = dsl, acc_z4_cnt = acc_z4_cnt, acc_z5_cnt = acc_z5_cnt, acc_z6_cnt = acc_z6_cnt, dec_z4_cnt = dec_z4_cnt, dec_z5_cnt = dec_z5_cnt, dec_z6_cnt = dec_z6_cnt),
      muscle_load = calc_load_scale(muscle_score),
      impact_score = calc_gk_impact_score(impact_z3 = impact_z3, impact_z4 = impact_z4, impact_z5 = impact_z5, impact_z6 = impact_z6),
      impact_load = calc_load_scale(impact_score),
      total_load = (muscle_load + speed_load + impact_load ) / 3
    ) %>% 
    select(
      position,
      name_display, 
      dur, 
      dur, 
      vel_max,
      dist,
      hsr_dist, 
      vel_z6_dist, 
      hml_dist, 
      exp_dist, 
      speed_load,
      dsl,
      muscle_load,
      impact_z46,
      impact_z56,
      impact_z6,
      impact_load,
      total_load,
      rpe
    )
  
   ssGoalKeeper %>% create_dtr_gk_reacttable()

 
```

GK Camp Overview
=====================================

row {data-height=4800}
-------------------------------------

### Goal Keeper Overview

```{r echo=FALSE, message=FALSE, warning=FALSE}

  #Create Plotly Of Camp

   mNames <- c(
      "Working Time",
      "Max Speed",
      "Total Dist",
      "High Int Dist",
      "Sprint Dist",
      "Intensive Dist",
      "Muscle Load",
      "Acc/Dec Dist",
      "Impacts z4-6",
      "Impacts z5-6",
      "Impacts z6"
    )

  ssGoalKeeper <- ssSession %>% 
    filter(position == 'GK') %>%
    mutate(acc_dec_cnt = acc_cnt + dec_cnt) %>%
    rename(
      `Athlete Name` = name_display,
      `Working Time` = dur_drill,
      `Max Speed` = vel_max,
      `Total Dist` = dist,
      `High Int Dist` = hsr_dist,
      `Sprint Dist` = vel_z6_dist,
      `Intensive Dist` = hml_dist,
      `Muscle Load` = dsl,
      `Acc/Dec Dist` = exp_dist,
      `Impacts z4-6` = impact_z46,
      `Impacts z5-6` = impact_z56,
      `Impacts z6` = impact_z6
    ) %>%
    select(`Athlete Name`, drill_date, sess_type, session_title, all_of(mNames)) %>% 
    pivot_longer(., cols = all_of(mNames), names_to = 'metric') 
  
    ssGK <- list()
    
    ssGK$time <- ssGoalKeeper %>% filter(metric == 'Working Time') %>% SharedData$new(., ~`Athlete Name`, group = "GK Athlete")
    ssGK$vel <- ssGoalKeeper %>% filter(metric == 'Max Speed') %>% SharedData$new(., ~`Athlete Name`, group = "GK Athlete")
    ssGK$dist <- ssGoalKeeper %>% filter(metric == 'Total Dist') %>% SharedData$new(., ~`Athlete Name`, group = "GK Athlete")
    ssGK$hsr <- ssGoalKeeper %>% filter(metric == 'High Int Dist') %>% SharedData$new(., ~`Athlete Name`, group = "GK Athlete")
    ssGK$sprint <- ssGoalKeeper %>% filter(metric == 'Sprint Dist') %>% SharedData$new(., ~`Athlete Name`, group = "GK Athlete")
    ssGK$hml <- ssGoalKeeper %>% filter(metric == 'Intensive Dist') %>% SharedData$new(., ~`Athlete Name`, group = "GK Athlete")
    ssGK$dsl <- ssGoalKeeper %>% filter(metric == 'Muscle Load') %>% SharedData$new(., ~`Athlete Name`, group = "GK Athlete")
    ssGK$exp <- ssGoalKeeper %>% filter(metric == 'Acc/Dec Dist') %>% SharedData$new(., ~`Athlete Name`, group = "GK Athlete")
    ssGK$iz46 <- ssGoalKeeper %>% filter(metric == 'Impacts z4-6') %>% SharedData$new(., ~`Athlete Name`, group = "GK Athlete")
    ssGK$iz56 <- ssGoalKeeper %>% filter(metric == 'Impacts z5-6') %>% SharedData$new(., ~`Athlete Name`, group = "GK Athlete")
    ssGK$iz6 <- ssGoalKeeper %>% filter(metric == 'Impacts z6') %>% SharedData$new(., ~`Athlete Name`, group = "GK Athlete")
     
    make_gk_plot <- function(df){
      plot_ly(data = df) %>% 
        add_trace(
            x = ~drill_date, 
            y = ~round(value,0),
            marker = list(color = '#18233F'),
            type = "bar",
            showlegend = F,
            hovertext = ~glue("
              Athlete: {`Athlete Name`}
              Metric: {metric}
              Type: {sess_type}
            ")
          ) %>% 
          layout(
            title = ~unique(`Athlete Name`),
            yaxis = list(title = ~unique(metric)),
            xaxis = list(title = "")
          )
    }
    
    p <- map(.x = ssGK, .f = ~make_gk_plot(.x))
    f <- filter_select("athleteName", "Athlete Name", ssGK$time, ~`Athlete Name`, multiple = F)


   
    bscols(widths = c(12), list(
      bscols(widths = c(3),f),
      bscols(widths = c(12),p)
    ))


  
```

```{js}
function filter_default() {
    document.getElementById("athleteName").getElementsByClassName("selectized")[0].selectize.setValue("Chituru Odunze", false);
}
window.onload = filter_default();
```

